\documentclass[10pt, letterpaper]{article}

% Packages:
\usepackage[
    ignoreheadfoot,
    top=1.5cm,
    bottom=1.5cm,
    left=1.5cm,
    right=1.5cm,
    footskip=0.5cm
]{geometry}
\usepackage{titlesec, tabularx, array, enumitem, fontawesome5, amsmath, hyperref, bookmark, lastpage, changepage, paracol, ifthen, needspace, iftex}
\usepackage[dvipsnames]{xcolor}
\definecolor{primaryColor}{RGB}{0, 102, 204}
\definecolor{sectionColor}{RGB}{0, 51, 102}
\hypersetup{
    colorlinks=true,
    urlcolor=primaryColor
}
\usepackage{charter}

% Formatting:
\raggedright
\pagestyle{empty}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\pagenumbering{gobble}
\titleformat{\section}{\color{sectionColor}\needspace{4\baselineskip}\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule]
\renewcommand{\labelitemi}{\textcolor{primaryColor}{\faCircle}}

% Reduce spacing for itemize
\setlist[itemize]{topsep=2pt, partopsep=0pt, itemsep=2pt, leftmargin=10pt}

\begin{document}

\begin{center}
    {\fontsize{22pt}{22pt}\selectfont \textcolor{primaryColor}{Mohamed Fahim}}\\
    \vspace{3pt}
    {\textcolor{sectionColor}{4th Year Computer Science Engineering Student}}\\
    \vspace{3pt}
    \href{tel:+918129640250}{+91 8129640250} \quad
    \href{mailto:contact@mdfahim.in}{contact@mdfahim.in} \quad
    \href{https://github.com/fai-max}{GitHub: @fai-max} \quad
    \href{https://www.linkedin.com/in/mohamed-fahim-79308829a}{LinkedIn}
\end{center}

\section{Education}
\textbf{Vellore Institute of Technology} (B.Tech, Computer Science)\hfill 2021 - Present, Chennai\\
\textit{CGPA: 8.25 /10}

\textbf{Sri Chaitanya Techno School} (Higher Secondary)\hfill 2019 - 2021, Chennai\\
\textit{Percentage: 93.4\% (CBSE)}

\textbf{The Pupil Saveetha Eco School} (10th Grade)\hfill 2016 - 2019, Chennai\\
\textit{Percentage: 84.4\% (CBSE)}

\section{Experience}
\textbf{TANGEDCO (TNEB) / Sponsored Project}\hfill August 2024 - Present, Chennai\\
Developing an Android app for employees to manage substation asset data offline with seamless synchronization.

\textbf{Mafkin Robotics / Video Editing \\& Graphic Design Intern}\hfill June - September 2024, Chennai\\
Hands-on experience with Blender and DaVinci. Successfully completed tasks, demonstrating dedication and curiosity.

\textbf{TechMahindra / Project Intern}\hfill August - October 2023, Bangalore\\
Developed a recruitment automation system using NLP, AI-driven interview scheduling, and automated candidate evaluation.

\section{Projects}
\textbf{Booth Calculator} (Self-Developed)\\
Developed a Booth’s algorithm-based multiplier with an intuitive UI and real-time binary conversion visualization.

\textbf{Glug.} (Ongoing)\\
An iOS app promoting hydration through short video shares, leaderboards, badges, and challenges.

\section{Skills}
\textbf{Technologies:} NumPy, Pandas, Tkinter, Discord.py, Django, SpaCy, OpenCV, PyAudio, Android Studio\\
\textbf{Languages:} Python, Java, C/C++, JavaScript, HTML, CSS, SwiftUI\\
\textbf{Databases:} MySQL, SQLite\\
\textbf{Tools:} Linux (Fedora, Ubuntu), Git, GitHub\\
\textbf{Coursework:} Machine Learning, Cryptography, IoT, DSA, OOP, MATLAB, RStudio

\section{Personal Development}
\begin{itemize}
    \item Proficient in video editing and design using Adobe tools and Blender.
    \item Media Head in The Linux Club, FilmSoc, and VRClub.
\end{itemize}

\section{Languages}
English, Hindi, Tamil, Malayalam, French, German

\end{document}
